---
title: "Untitled"
author: "Cherin-Juliette"
date: '2022-05-27'
output: 
  html_document:
    toc: true
    toc_float: true
---
<br>

```{r}
library(magrittr)     ## pipeline %>% shortcut with ctrl + alt + m
library(tidyverse)
library(ggplot2)      ## data visualization 
library(png)          ## combining .png extension images
devtools::load_all()
```


#### **Electricity boxes in the city center**
Initiative of the city ambassador group Thirty030. Electricity boxes around the city have been transformed by 18 artists.
```{r}
## Hex codes detected with the ginifab.com site
binnenstad_patatjes4life_2021 <- c("#fc84e8", 
                                   "#be32bb", 
                                   "#c999bf", 
                                   "#106dc2", 
                                   "#129bfe", 
                                   "#4e74a7", 
                                   "#fcab4d", 
                                   "#413b43", 
                                   "#d6c840", 
                                   "#33783a", 
                                   "#44553a", 
                                   "#457666")

## Putting hex codes into a bar chart using the mpg dataset
df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "patatjes4life")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: patatjes4life")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")

pl2


## combining the original image with the bar chart image



```

#### **Phase contrast microscope mural in the Stroweg**
Women physicist and maker of the phase contrast microscope was an alumni of the Utrecht University.
```{r}
strosteeg_destrakkehand_2021 <- c("#182c4b", 
                                  "#091527", 
                                  "#274d78", 
                                  "#333f56", 
                                  "#7f92ad", 
                                  "#5a2f2b", 
                                  "#7b4003", 
                                  "#7d4e0d", 
                                  "#8da17e", 
                                  "#34512a")

df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "microscope")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: microscope")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2

```

#### **Groceries mural above the Albert Heijn on Amsterdamsestraatweg 367**
```{r}
amsterdamsestraatweg367_janisdeman_2021 <- c("#2f2332", 
                                             "#594476", 
                                             "#871a2d", 
                                             "#c83a24", 
                                             "#eb813a", 
                                             "#29432a", 
                                             "#7c923a", 
                                             "#596365", 
                                             "#fddd29")


df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "ah")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: ah")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **Rainbow crosswalk at the Uithof, in front of the University of Applied Sciences**
```{r}
uithof_hu_2021 <- c("ff0000",
                    "#1a9fd9",
                    "ffa500", 
                    "ffff00", 
                    "008000", 
                    "0000ff", 
                    "4b0082", 
                    "4b0082", 
                    "ee82ee", 
                    "cc99c9", 
                    "9ee09e", 
                    "#84674d", 
                    "#1870d5")


df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "hu")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: hu")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2

```

#### **Vogelenbuurt mural by Jan is de Man**
```{r}
vogelenbuurt_janisdeman_2020 <- c("#016258", 
                                  "#008f89", 
                                  "#51bfa7", 
                                  "#41bbb0", 
                                  "#159ec6", 
                                  "#06507d", 
                                  "#1b1f3c", 
                                  "#be8b4e", 
                                  "#d15a3a", 
                                  "#043229", 
                                  "#5f1944")


df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "vogelenbuurt")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: vogelenbuurt")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **Geese mural on the Gansstraat 64 by De Strakke Hand**
```{r}
gansstraat64_destrakkehand_2020 <- c("8cd3ff", 
                                     "#009dff", 
                                     "#454147", 
                                     "#7d0e20", 
                                     "#393d20", 
                                     "#7f883c", 
                                     "#413014", 
                                     "f9c70c")
```

#### **3D street art at Berlijnplein by Leon Keer**
```{r}
berlijnplein_leonkeer_2020 <- c("#91030e", 
                                "#d83a55", 
                                "#a55d6d", 
                                "#c47b89", 
                                "#745563", 
                                "#5a3659", 
                                "#2e2c2b", 
                                "#48735a", 
                                "#6a9098", 
                                "#976557")


df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "organs")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: organs")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **Mural on the Ibis Hotel on Bizetlaan by De Strakke Hand**
```{r}
bizetlaan_destrakkehand_2019 <- c("603c14",
                                  "9c2706",
                                  "d45b12",
                                  "#ac4649",
                                  "f4af28",
                                  "c17f29",
                                  "#185aa0",
                                  "b29804",
                                  "bfe6ff",
                                  "acdf87",
                                  "1a8693")


df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "ibis_hotel")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: ibis_hotel")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **The Wale at the Tivolivredenburg by Studio KCA**
```{r}
tivolivredenburg_studiokca_2018 <- c("#021c95", 
                                     "#2078c4", 
                                     "#178ec7", 
                                     "#44a9bb", 
                                     "#249780", 
                                     "#6a9a8a", 
                                     "#efa548", 
                                     "#7b5d53")


df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "the_wale")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: the_wale")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **The Derk on Lauwerecht 55 by Derk Wessels and Jan is de Man**
```{r}
lauwerecht55_derkwessels_2018 <- c("#673042", 
                                   "#8a2746", 
                                   "#e7788a", 
                                   "#d88a98", 
                                   "#141d02", 
                                   "#59644b", 
                                   "#b1bd4d", 
                                   "#1a2f4a", 
                                   "#3094b2", 
                                   "#2f1f0d", 
                                   "#393842")


df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "derk_wessels")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: derk_wessels")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **Miffy by Dick Bruna**
```{r}
mariaplaats_destrakkehand_2017 <- c("#1B549A",
                                    "#30702F",
                                    "#FAC700",
                                    "#ED4C06",
                                    "#DD3E0E",
                                    "#914D23",
                                    "#DADADA",
                                    "#202221")


df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "miffy")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: miffy")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **Dichterswijk by Munir de Vries**
```{r}
dichterswijk_munirdevries_2017 <- c("#0c454b",
                                    "#13755e",
                                    "#4ebf93",
                                    "#6b181a",
                                    "#ac2b1c",
                                    "#fd5e14",
                                    "#edc67c",
                                    "#3b2046",
                                    "#683e68",
                                    "#733d49",
                                    "#97554f")



df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "poet_district")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: poet_district")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **Trains at Meidoornstraat by De Verfdokter**
```{r}
meidoornstraat_verfdokter_2015 <- c("#1b3318",
                                    "#29533e",
                                    "#3f7d2e",
                                    "#898327",
                                    "#c8b862",
                                    "#99262c",
                                    "#f65066",
                                    "#1662a5",
                                    "#3c7cad",
                                    "#58a4d2")



df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "trains")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: trains")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **De Wonderen/The Wonders on Langenoord by Boukje Lootsma**
```{r}
langenoord_boukjelootsma_2014 <- c("#0e120c",
                                    "#213526",
                                    "#505231",
                                    "#524434",
                                    "#b05c65",
                                    "#d88e99",
                                    "#bc8eb6",
                                    "#bb8cc3",
                                    "#9b6c61",
                                    "#727e8f",
                                    "#626514",
                                    "#455c17",
                                    "#daae52")



df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "the_wonders")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: the_wonders")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **Ducdalf Met Schepen/ Ships with Ducdalf on Adelaarsstraat by Anne P. Boer**
```{r}
adelaarsstraat_anneboer_1978 <- c("#c91f40",
                                  "#8f475b",
                                  "#523e32",
                                  "#7d3c3a",
                                  "#994745",
                                  "#c1a2a7",
                                  "#e26a3b",
                                  "#84658b",
                                  "#885f80",
                                  "#9484a1",
                                  "#cc9f5c",
                                  "#70a3b7",
                                  "#97c7d6")



df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "ships_with_ducdalf")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: ships_with_ducdalf")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

#### **Utrecht University on the Domplein**
```{r}
domplein_uu <- c("#fac902",
                 "#b70a28",
                 "#030203",
                 "#653a15",
                 "#303810",
                 "#485c08")



df <- mpg %>%
  dplyr::group_by(manufacturer) %>%
  dplyr::mutate(manufacturer = str_to_title(manufacturer))%>%
  tally()

df

pl2 <- ggplot(data = df,aes(x= reorder(manufacturer, - n), y = n,fill = manufacturer))
pl2 <- pl2 + geom_bar(stat = "identity")
pl2 <- pl2 + geom_text(aes(label = n), size =  2, vjust = -0.3)
pl2 <- pl2 + theme_classic() + scale_fill_rcolorUtrecht(palette = "uu")
pl2 <- pl2 + labs(x = "Car Manufacturers", y= "Number of Models")
pl2 <-pl2 + labs(title = "Palette: uu")
pl2 <- pl2 + labs(subtitle = "Shown in descending order of  number of models")
pl2 <- pl2 + labs(caption = "Data: mpg dataset ")
pl2 <- pl2 + ggeasy::easy_rotate_labels(which = "x", angle = 90)
pl2 <- pl2 + theme(legend.position ="none")


pl2
```

